---
title: "Berkson’s Bias: Offensive Rating and Height in NCAA and NBA Basketball"
format: html
---

```{r setup, include=FALSE}

pacman::p_load(learnr, tidyverse, stats, knitr, gridExtra)

###import the dataset here

```
## Welcome 

Please watch this intro video from ________ to learn more about the question we'll be investigating today!

</iframe>

## Background 

This lesson will focus on the correlation between offensive rating and height. We will be begin by exploring the data and conducting some descriptive analysis and visualizations. Then we will answer our question using a linear regression. 

And in this process we will___

## Basketball Basic 

If you aren't familiar with Basketball, consider watching this [This is an introduction video]

In a typical professional basketball game there are two teams of 5 people trying to put the basketball in the basketball hoop to score points and to see who has more points at the end of 2 20 minute halfs. 

Add more information about basketball basics that are important

### Offensive Rating - Nate

To understand what is Offensive rating is in basketball it is important to understand what Per 100 Possession stats are since Offensive rating is build on per 100 possession stats.

First lets define what a possession, a possession is everytime a player does one of four things: attempts a field goal, misses a shot and does not get the offensive rebound, turns the ball over, and goes to the foul line for 2 or 3 free throws. Now basketball is a very unfair sport in the sense that there is 10 players on the court at a time and only one ball so some players are going to have more possessions with the ball than other players leading to them having more possessions and thus a better per possession statistical line as they have had more opportunities with the ball. To balance this out basketball statistions have created something know as Per 100 Possession stats in which it looks at a players stats if they had 100 possessions. This creates a equal way to compare players as now every player has ben put on the same baseline.

Now that we have defined what Per 100 Possession is lets define what Offensive rating is and how it builds off of Per 100 Possession. Offensive rating is the number of points produced by a player per 100 total individual possessions. In other words it mean how many points would a player score in 100 possessions. To calculate this we find how many points a player produces divdied by his total possessions then multiply by 100. This gets us offensive rating which uses per 100 possession stats to create a wholestic statistical variable that allows us to judge a players overall offensive abilities compared to other players. The larger the number the more points they would score given 100 possessions. 


## Data Exploration and Descriptive Analysis 


```{r head, exercise = TRUE, exercise.eval = FALSE}
# Print the (first 1000 rows of) the data


# Get a summary of the data


```

add code that asks questions about the dataset and what certain things meaning. 5 multiple choice questions


### Offensive Rating and Height Correlation 
offensive rating blah blah

code for the graph

code for a question about the graph 


## Berkson's Bias _ Ricky


### Analyzing NBA Draftees using Linear Regression 

### Interpreting the Graph Results and Berkson's Bias

## Conclusion 

### Berkson's Bias and College Basketball Players

### Statistical Lesson
